Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-13 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add to introduction. Add references

@@

@@

Currently, distance parameters involved with assessing risk of a particular storm have been rather arbitrary, contributing to the necessity in understanding how such parameters influence a county's exposure status. In assessing the risk of a given storm based on distance, recent studies have defined the distance from the storm track affected by a given storm differently. [@Czajkowski2011] assessed county-level risk and exposure based on a three-tierd definition, with primary counties being those closest to the storm track on either side, secondary counties being adjacent to primary coutnies, and tertiary counties adjacent to secondary counties. Such a defenition resulted in an exposure defenition based on an average distance radius of 120 km on either side of the storm track [@Czajkowski2011]. 
#### Rain-based exposure

>>>>

Current hurricane exposure assignments are often nonspecific and may lead to missclassification of exposure at the county-level [@Grabich2016]. Such missclassification can have important public health and economic implications.

Studies have begun to assess county-level hurricane exposure using large historical datasets [@Zandbergen2009] ... making the `hurricaneexposure` package a powerful tool in future exposure analysis.

@@

[@Zandbergen2009] developed an exposure factor based on location (longitude and latitude), county shape, county size, and distance from the coast.

@@

Currently, distance parameters involved with assessing risk of a particular storm have been rather arbitrary, contributing to the necessity in understanding how such parameters influence a county's exposure status. In assessing the risk of a given storm based on distance, recent studies have defined the distance from the storm track affected by a given storm differently. [@Czajkowski2011] assessed county-level risk and exposure based on a three-tierd definition, with primary counties being those closest to the storm track on either side, secondary counties being adjacent to primary coutnies, and tertiary counties adjacent to secondary counties. Such a defenition resulted in an exposure defenition based on an average distance radius of 120 km on either side of the storm track [@Czajkowski2011]. Such a distance is slightly greater than that commonly used by public health departments (i.e., 100 km) [@Czajkowski2011]. In other cases, distance has been defined on the basis of maximum sustained wind speeds and their decay, with exposure defined as those counties exposed to wind speeds greater than or equal to tropical storm strength (39--73 miles per hour) [@Zandbergen2009] and may not provide an accurate respresentation of the communities exposed to a given storm (e.g., a large number of inland counties are likely underrepresented under this definition).  
#### Rain-based exposure
